\trtitle\\[0.3cm]{\normalsize\trtype}

### 2024-01-28 Paper/main.tex
Final paper version

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Additional 'theorem' and 'definition' blocks:
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
%\newtheorem{theorem}{Satz}[section]		% Wenn in Deutsch geschrieben wird.
\newtheorem{axiom}{Axiom}[section] 	
%\newtheorem{axiom}{Fakt}[chapter]			% Wenn in Deutsch geschrieben wird.
%Usage:%\begin{axiom}[optional description]%Main part%\end{fakt}

@@

%Additional types of definitions:
\theoremstyle{remark}
%\newtheorem{remark}[definition]{Bemerkung} % Wenn in Deutsch geschrieben wird.
\newtheorem{remark}[definition]{Remark}

@@

The following presents the possibility and methodology of using \ac{DDPM} to generate novel designs for Pokémons. Firstly, previous approaches and their used models are presented in Section \ref{sec:relwork}. Following, the methodology is described namely the model architecture in Section \ref{sec:model} and \ref{sec:dataAca_and_preprocessing}. Finally, the results are presented and discussed in Section \ref{sec:results} and \ref{sec:discussion}. Section \ref{sec:conclusion} presents the shortcomings of this study and what can be improved upon. 
%
%
\section{Related Work}
\label{sec:relwork}
The following section is divided into two. Firstly, related works regarding \ac{GAN}s are discussed with a closer look into the current uses of \ac{DDPM}s. Secondly, previous approaches using \ac{GAN}s to create new images of Pokémon are analyzed. 
There are multitudes of variation of \ac{GAN}s, with notable architectures like \ac{DCGAN} \citep{Radford2016}, StyleGAN \citep{Karras2019}, and BigGAN \citep{Brock2019}. While all of these models have the same underlying purpose, i.e. generating novel images based on an existing data pool, their architecture has been optimized for a specific task. For example the StyleGan architecture is used for combining images, often applying certain features of one image onto another \citep{Karras2019}. In contrast, the BigGan architecture is used to enhance the quality of images often up-scaling low resolution images to a higher resolution \citep{Brock2019}. \\
Given their ability to model intricate patterns and dependencies within data \ac{DDPM}s have been employed in various tasks. For example, image translation \citep{Sasaki2021}, inpainting \citep{Lugmayr2022} or image restoration \citep{Nair2023}. \ac{DDPM}s have also been used beyond image generation, examples are feature extraction \citep{Bandara2024}, anomaly detection \citep{Wyatt2022} and time-series forecasting \citep{Rasul2021}. Given their variability in use-cases \ac{DDPM}s are a good fit for generating new Pokémon designs. \\

@@

\section{Model}
\label{sec:model}
The model employed was based on the \ac{DDPM} presented by \cite{Ho2020}. \cite{Ho2020} presents both an unconditional Model and a conditional one. For generating the images we only employed the conditional architecture. However, the architecture was slightly modified. The most significant change was the implementation of a scale factor which gives the ability to increase/decrease the amount of model parameters.

\ac{DDPM} are a class of generative models that aim to model the data distribution by defining a diffusion process. The primary idea behind \ac{DDPM}s is to transform a simple distribution (e.g., a Gaussian distribution) into the target data distribution through a series of carefully designed transformations. This diffusion process is done step-by-step slowly transforming the input noise to an image resembling the training data. \\
At each step of the diffusion process, a noise is added to the data, and the data is transformed to a new state. This process is repeated multiple times until the input noise has been transformed to an image resembling the training data. \\
The model is trained by optimizing its parameters to maximize the likelihood of the observed data. During training, the model learns the transformations that map the simple initial distribution to the target data distribution. This involves adjusting the parameters in a way that the generated samples match the characteristics of the training data.\\
Once trained, the DDPM can generate new samples by starting with samples from the simple initial distribution and applying the learned reverse transformations in the reverse order.\\

Overall, DDPMs provide a probabilistic framework for generative modeling, leveraging a diffusion process to model the transformation from a simple distribution to a complex data distribution. This allows them to capture intricate patterns and dependencies in the data.

@@

We collected links for each entry, simplifying the retrieval of all accessible images through a systematic naming convention. The link structure is as follows: "pokemondb.net/identifier/Pokémon." Changing the identifier granted access to two distinct datasets. The "artwork" identifier encompassed both official and alternative artwork, while the "sprites" section stored all in-game renditions of the Pokémon. In total, we obtained 26,896 unique images (22,825 sprites and 4,071 artworks). The term "unique" requires caution, as we intentionally included both male and female versions (even if differing by minor details) and normal and shiny versions (same Pokémon but with different color coding). Additionally, the database provides GIFs depicting the idle animation of the Pokémon. Each frame of these animations were added to the dataset. The back view of Pokémon were ignored since the goal was to generate images from the front.

@@

Note that the trained model is a conditional diffusion model, thus the samples should be categorized in a logical scheme.  There are multiple approaches on how the samples can be grouped. Typically, Pokémon are grouped based on their typing \footnote{Typing refers to the elemental or thematic category (fire, water, ghost, fairy etc.) that a Pokémon belongs to. Each Pokémon has one or two types, which determine its strengths and weaknesses in battles. There are 18 different types in total, and each type has its own set of interactions with other types.}. However, optimally similar images are grouped together. Pokémon belonging to the same type can differ drastically in regards to their appearance. Therefore, we opted to group samples based on the body from the Pokémon. 
This resulted in following classes.\\

@@

\begin{multicols}{3}
	\begin{enumerate}[itemsep=2pt,parsep=2pt]
		\item only a head
		\item a head and legs
		\item fins
		\item insectoid body
		\item quadruped body
		\item single pair of wings
		\item multiple bodies
		\item tentacles
		\item base and legs
		\item bipedal with tail
		\item bipedal without tail
		\item two or more pairs of wings
		\item serpentine body
		\item a head and arms
	\end{enumerate}
\end{multicols}

@@

\subsection{Preprocessing}
The next problem we encountered was the difference in their background, their image mode and
type. At first we resize every image to 64x64. The original artwork and sprites were all transparent ”.png”, meaning they have no background and therefore a fourth channel encoding the transparency of the given pixel. This fourth channel resulted in partially transparent Pokémon and added unnecessary parameters to the network. Therefore we converted each of the ”RGBA”
images to uniform ”RGB” images with a white background to keep their characteristic black outlining. \\
As the alternative artworks were collected from a variety of different artists there was no convention resulting in different file types (jpg, jpeg and vector png), backgrounds and image modes.
To keep the format we established in the previous step we again removed the additional transparency channel and converted each image to png. Additionally, we detected each image which did not have a white background and adjusted it accordingly.\\
 Moreover, was there a difference
in coverage of the image. While the artworks used all available space of the image the sprites only used around 10\% therefore exposing a lot of white background. This was apparent after training a few test epochs which resulted in solely white images with a small focus somewhere in the center (which was no surprise as the sprites represented the majority of the dataset). To counteract this, we located the focus point of the image (location of Pokémon) by removing
each row/column only containing white pixels. Then to avoid morphing the shape of the Pokémon we padded it to a square. At last we again resized the cropped image to get a uniform size of 64x64 pixels.\\
The code for making the images uniform can be found \href{https://github.com/mhueppe/Diffusion_Models/blob/master/preprocessing/preprocessing_uniform_data.py}{here}.

@@

\subsection{\ac{CIFAR-10}}\label{sec:results:cifar10}
To validate the model pipeline we first trained the model on the \href{https://www.cs.toronto.edu/~kriz/cifar.html}{\ac{CIFAR-10}} dataset since the model has already reported good results on this data. The \ac{CIFAR-10} dataset is a collection of 60,000 32x32 color images in 10 different classes, with 6,000 images per class. Each image belongs to one of the following classes:

@@

Similarly, our model reported good results as well.

@@

@@

The displayed examples in Figure \ref{fig:pokemonperbodytype} depict that the model is generally able to generate Pokémon for a given body type. The samples were grouped to maximize the similarity within a class and the difference between two classes. However, Pokémon expressed their associated body type to various degrees blurring the lines between classes and decreasing the similarity within a class. \\
The following phenomena were found regardless of dataset: Even though the \ac{MSE} was not steadily decreasing after a certain amount of time the generated images were still improving. The quality of images was dependent on the class were images for some classes were more indicative of the training images than other classes. The images that showed the highest image quality for the \ac{CIFAR-10} dataset were images belonging to the class car, truck and ship. For the Pokémon dataset the body types showing the highest quality in generated images were single/multiple pair of wings and only head. Additionally, no significant difference in quality between images generated using \ac{EMA} compared to images where \ac{EMA} was not used can be seen. This is depicted in Figure \ref{fig:cifar10results}.

A known problem with \ac{GAN}s is mode collapse. This phenomenon describes models which focus on the most common feature in the dataset to generate new images. Instead of generating diverse samples that cover the entire data distribution, the generator might focus on generating samples with certain features. This lack of diversity in the generated data can be seen in the class "only head".\\
This category includes the Pokémon "Unknown", which mimics the Latin alphabet and thus has 28 variations. Though different, all variations follow the same design rules, black lines and one eye. Accounting for all different image types 53\% of the images in this category were just depicting some variation of this Pokémon. This can be seen in the results generated for this class. Mainly, most of th generated images follow the "Unknown" design. Examples can be seen in Figure \ref{fig:unknownvariety}. This mode collapse can be avoided by filtering the images within the class.\\
This can be avoided by using sub sampling i.e. train more on the Pokémons in this category that are represented less.

Moreover, there is a noticeable difference in the coherence of images among classes. Images generated for a specific class exhibit greater similarities, whereas other classes display a higher variance in the generated images. This is illustrated in Figure \ref{fig:}. The samples generated for the class "quadrupled" differ more strongly in comparison to images generated for the class "winged".

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\linewidth]{src/Images/head_generated}
	\caption[Generated images for head]{Different generated images for the head category. It can be seen that the model replicates the design of the Pokémon "Unknown".}
	\label{fig:unknownvariety}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{src/Images/category_comparison}
	\caption[Class Comparison]{Comparison between classes}
	\label{fig:categorycomparison}
\end{figure}

\section{Conclusion}
\label{sec:conclusion}

While the model was overall successful in generating Pokémon based on body type, the training was mainly impeded by the lack of hardware. The model was trained using an NVIDIA GeForce GTX 1650 with 4GB of dedicated GPU memory. This allowed only images of the size 34x34 to be trained on and generated. Additionally, the biggest batch size without exceeding the available space was 8 samples, which increased the training time and hindered the model from training on multiple samples at once. Future studies should aim to increase the size of the images to be trained on.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% hier werden - zum Ende des Textes - die bibliographischen Referenzen
% eingebunden
%
% Insbesondere stehen die eigentlichen Informationen in der Datei
% ``bib.bib''
%
\newpage
\printbibliography[heading=bibintoc]

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Additional 'theorem' and 'definition' blocks:
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
%\newtheorem{theorem}{Satz}[section]		% Inn in Deutsch geschrieben wird.
\newtheorem{axiom}{Axiom}[section] 	
%\newtheorem{axiom}{Fakt}[chapter]			% Inn in Deutsch geschrieben wird.
%Usage:%\begin{axiom}[optional description]%Main part%\end{fakt}

@@

%Additional types of definitions:
\theoremstyle{remark}
%\newtheorem{remark}[definition]{Bemerkung} % Inn in Deutsch geschrieben wird.
\newtheorem{remark}[definition]{Remark}

@@

The following presents the possibility and methodology of using \ac{DDPM} to generate novel designs for Pokémons. Firstly, previous approaches and their used models are presented in Section \ref{sec:relwork}. Following, the methodology is described namely the model architecture in Section \ref{sec:model} and the data acquisition and processing Section \ref{sec:dataAca_and_preprocessing}. Finally, the results are presented and discussed in Section \ref{sec:results} and \ref{sec:discussion}. Section \ref{sec:conclusion} presents the shortcomings of this study and what can be improved upon. 
%
%
\section{Related Work}
\label{sec:relwork}
The following section is divided into two. Firstly, related works regarding \ac{GAN}s are discussed with a closer look into the current uses of \ac{DDPM}s. Secondly, previous approaches using \ac{GAN}s to create new images of Pokémon are analyzed. 
There are multitudes of variation of \ac{GAN}s, with notable architectures like \ac{DCGAN} \citep{Radford2016}, StyleGAN \citep{Karras2019}, and BigGAN \citep{Brock2019}. While all of these models have the same underlying purpose, i.e. generating novel images based on an existing data pool, their architecture has been optimized for a specific task. For example the StyleGan architecture is used for combining images, often applying certain features of one image onto another \citep{Karras2019}. In contrast, the BigGan architecture is used to enhance the quality of images often up-scaling low resolution images to a higher resolution \citep{Brock2019}. \\
Given their ability to model intricate patterns and dependencies within data \ac{DDPM}s have been employed in various tasks. For example, image translation \citep{Sasaki2021}, inpainting \citep{Lugmayr2022} or image restoration \citep{Nair2023}. \ac{DDPM}s have also been used beyond image generation, examples are feature extraction \citep{Bandara2024}, anomaly detection \citep{Wyatt2022} and time-series forecasting \citep{Rasul2021}. Given their variability in use-cases \ac{DDPM}s are a good fit for generating new Pokémon designs. \\

@@

\section{Model}
\label{sec:model}
The model employed was based on the \acf{DDPM} presented by \cite{Ho2020} who presents both an unconditional Model and a conditional one. For generating the images I only employed the conditional architecture. However, the architecture was slightly modified. The most significant change was the implementation of a scale factor which gives the ability to increase/decrease the amount of model parameters.

\ac{DDPM} are a class of generative models that aim to model the data distribution by defining a diffusion process. The primary idea behind \ac{DDPM}s is to transform a simple distribution (e.g., a Gaussian distribution) into the target data distribution through a series of carefully designed transformations. This diffusion process is done step-by-step slowly transforming the input noise to an image resembling the training data. \\
At each step of the diffusion process, a noise is added to the data, and the data is transformed to a new state. This process is repeated multiple times until the input noise has been transformed to an image resembling the training data. \\
The model is trained by optimizing its parameters to maximize the likelihood of the observed data. During training, the model learns the transformations that map the simple initial distribution to the target data distribution. This involves adjusting the parameters in a way that the generated samples match the characteristics of the training data.\\
Once trained, the DDPM can generate new samples by starting with samples from the simple initial distribution and applying the learned reverse transformations in the reverse order.\\
Overall, DDPMs provide a probabilistic framework for generative modeling, leveraging a diffusion process to model the transformation from a simple distribution to a complex data distribution. This allows them to capture intricate patterns and dependencies in the data.\\

The diffusion model approach can be used in combination with a multitude of model architectures. The most common and the model used by us was the U-Net as presented by \cite{Ronneberger2015}. \\
The U-Net is named after the shape of the models' architecture. As a \ac{DDPM} the U-Net aims to predict noise, to achieve this it creates a feature map for the input image. Using convolutions and max-pooling the resolution of the feature map is decreased at each step. This resembles the idea of a decoder to break down each image into it's most important components. Similarly, the U-Net implements an encoding process where resolution of the previously reduced feature map are then increased to replicate an image from decoding noise. This is done by using up-convolutions. Additionally, the U-Net implements skip connections at each resolution change. An original illustration of the U-Net is depicted in Figure \ref{fig:unet}.\\

\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\linewidth]{src/Images/u_net}
	\caption[U-Net architecture]{U-Net architecture as presented by \cite{Ronneberger2015}.}
	\label{fig:unet}
\end{figure}

@@

I collected links for each entry, simplifying the retrieval of all accessible images through a systematic naming convention. The link structure is as follows: "pokemondb.net/identifier/Pokémon." Changing the identifier granted access to two distinct datasets. The "artwork" identifier encompassed both official and alternative artwork, while the "sprites" section stored all in-game renditions of the Pokémon. In total, I obtained 26,896 unique images (22,825 sprites and 4,071 artworks). The term "unique" requires caution, as I intentionally included both male and female versions (even if differing by minor details) and normal and shiny versions (same Pokémon but with different color coding). Additionally, the database provides GIFs depicting the idle animation of the Pokémon. The start and middle frame of these animations were added to the dataset. The back view of Pokémon were ignored since the goal was to generate images from the front.

@@

Note that the trained model is a conditional diffusion model, thus the samples should be categorized in a logical scheme.  There are multiple approaches on how the samples can be grouped. Typically, Pokémon are grouped based on their typing \footnote{Typing refers to the elemental or thematic category (fire, water, ghost, fairy etc.) that a Pokémon belongs to. Each Pokémon has one or two types, which determine its strengths and weaknesses in battles. There are 18 different types in total, and each type has its own set of interactions with other types.}. However, optimally similar images are grouped together. Pokémon belonging to the same type can differ drastically in regards to their appearance. Since the goal was to maximize the inner-class visual similarity and the between-class discrepancy, I opted to group samples based on the body from the Pokémon. 
This resulted in following classes.\\

@@

\begin{multicols}{3}
	\begin{enumerate}[itemsep=2pt,parsep=2pt]
		\item \href{https://bulbapedia.bulbagarden.net/wiki/List_of_Pok%C3%A9mon_by_shape#Pok.C3.A9mon_consisting_of_only_a_head}{only a head}
		\item \href{https://bulbapedia.bulbagarden.net/wiki/List_of_Pok%C3%A9mon_by_shape#Pok.C3.A9mon_consisting_of_a_head_and_legs}{a head and legs}
		\item \href{https://bulbapedia.bulbagarden.net/wiki/List_of_Pok%C3%A9mon_by_shape#Pok.C3.A9mon_with_fins}{fins}
		\item \href{https://bulbapedia.bulbagarden.net/wiki/List_of_Pok%C3%A9mon_by_shape#Pok.C3.A9mon_with_an_insectoid_body}{insectoid body}
		\item \href{https://bulbapedia.bulbagarden.net/wiki/List_of_Pok%C3%A9mon_by_shape#Pok.C3.A9mon_with_an_insectoid_body}{quadruped body}
		\item \href{https://bulbapedia.bulbagarden.net/wiki/List_of_Pok%C3%A9mon_by_shape#Pok.C3.A9mon_with_a_single_pair_of_wings}{single pair of wings}
		\item \href{https://bulbapedia.bulbagarden.net/wiki/List_of_Pok%C3%A9mon_by_shape#Pok.C3.A9mon_consisting_of_multiple_bodies}{multiple bodies}
		\item \href{https://bulbapedia.bulbagarden.net/wiki/List_of_Pok%C3%A9mon_by_shape#Pok.C3.A9mon_with_tentacles_or_a_multiped_body}{tentacles}
		\item \href{https://bulbapedia.bulbagarden.net/wiki/List_of_Pok%C3%A9mon_by_shape#Pok.C3.A9mon_consisting_of_a_head_and_a_base}{base and legs}
		\item \href{https://bulbapedia.bulbagarden.net/wiki/List_of_Pok%C3%A9mon_by_shape#Pok.C3.A9mon_with_a_bipedal.2C_tailed_form}{bipedal with tail}
		\item \href{https://bulbapedia.bulbagarden.net/wiki/List_of_Pok%C3%A9mon_by_shape#Pok.C3.A9mon_with_a_bipedal.2C_tailless_form}{ bipedal without tail}
		\item \href{https://bulbapedia.bulbagarden.net/wiki/List_of_Pok%C3%A9mon_by_shape#Pok.C3.A9mon_with_two_or_more_pairs_of_wings}{two or more pairs of wings}
		\item \href{https://bulbapedia.bulbagarden.net/wiki/List_of_Pok%C3%A9mon_by_shape#Pok.C3.A9mon_with_serpentine_bodies}{serpentine body}
		\item \href{https://bulbapedia.bulbagarden.net/wiki/List_of_Pok%C3%A9mon_by_shape#Pok.C3.A9mon_consisting_of_a_head_and_arms}{a head and arms}
	\end{enumerate}
\end{multicols}

@@

\subsection{Preprocessing}
The next problem I encountered was the difference in their background, their image mode and
type. At first I resize every image to 64x64. The original artwork and sprites were all transparent ”.png”, meaning they have no background and therefore a fourth channel encoding the transparency of the given pixel. This fourth channel resulted in partially transparent Pokémon and added unnecessary parameters to the network. Therefore I converted each of the ”RGBA”
images to uniform ”RGB” images with a white background to keep their characteristic black outlining. \\
As the alternative artworks were collected from a variety of different artists there was no convention resulting in different file types (jpg, jpeg and vector png), backgrounds and image modes.
To keep the format I established in the previous step I again removed the additional transparency channel and converted each image to png. Additionally, I detected each image which did not have a white background and adjusted it accordingly.\\
 Moreover, was there a difference
in coverage of the image. While the artworks used all available space of the image the sprites only used around 10\% therefore exposing a lot of white background. This was apparent after training a few test epochs which resulted in solely white images with a small focus somewhere in the center (which was no surprise as the sprites represented the majority of the dataset). To counteract this, I located the focus point of the image (location of Pokémon) by removing
each row/column only containing white pixels. Then to avoid morphing the shape of the Pokémon I padded it to a square. At last I again resized the cropped image to get a uniform size of 64x64 pixels.\\
The code for making the images uniform can be found \href{https://github.com/mhueppe/Diffusion_Models/blob/master/preprocessing/preprocessing_uniform_data.py}{here}.

@@

\subsection{\ac{CIFAR-10}}\label{sec:results:cifar10}
To validate the model pipeline I first trained the model on the \href{https://www.cs.toronto.edu/~kriz/cifar.html}{\ac{CIFAR-10}} dataset since the model has already reported good results on this data. The \ac{CIFAR-10} dataset is a collection of 60,000 32x32 color images in 10 different classes, with 6,000 images per class. Each image belongs to one of the following classes:

@@

Similarly, our model reported good results as Ill.

@@

A known problem with \ac{GAN}s is mode collapse \citep{Zhang2018}. This phenomenon describes models which focus on the most common feature in the dataset to generate new images. Instead of generating diverse samples that cover the entire data distribution, the generator might focus on generating samples with certain features. This lack of diversity in the generated data can be seen in the class "only head".\\
This category includes the Pokémon \href{https://bulbapedia.bulbagarden.net/wiki/Unown_(Pok%C3%A9mon)}{"Unown"}, which mimics the Latin alphabet and thus has 28 variations. Though different, all variations follow the same design rules, black lines and one eye. Accounting for all different image types 53\% of the images in this category were just depicting some variation of this Pokémon. This can be seen in the results generated for this class. Mainly, most of th generated images follow the "Unown" design. Examples can be seen in Figure \ref{fig:Unownvariety}.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\linewidth]{src/Images/unown_examples}
	\caption[Generated images for head]{Different generated images for the head category reminiscent of the Pokémon "Unown".}
	\label{fig:Unownvariety}
\end{figure}

Moreover, there is a noticeable difference in the coherence of images among classes. Images generated for a specific class exhibit greater similarities, whereas other classes display a higher variance in the generated images. This is illustrated in Figure \ref{fig:categorycomparison}. The samples generated for the class "quadrupled" differ more strongly in comparison to images generated for the class "winged".

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{src/Images/category_comparison}
	\caption[Class Comparison]{Comparison between classes "with wings" (left) and "bipedal without tail" (right).}
	\label{fig:categorycomparison}
\end{figure}

@@

The displayed examples in Figure \ref{fig:pokemonperbodytype} depict that the model is generally able to generate Pokémon for a given body type. The samples  were  grouped to maximize the similarity within a class and the difference between two classes. However, Pokémon expressed their associated body type to various degrees blurring the lines between classes and decreasing the similarity within a class. \\
Additionally, given the unbalanced nature of the dataset the model learned to focus on the Pokémon that  were  represented more often for the given class resulting in a mode collapse for the class "only head" as presented in Figure \ref{fig:Unownvariety}. The mode collapse can be avoided by filtering the images within the class or employing sub sampling i.e. train more on the Pokémons in this category that are represented less. 
Moreover, as shown in Figure \ref{fig:categorycomparison} the difference in inner-class variety was fairly high. If one wants to increase the similarity within a class other grouping methods can be of use. An additional approach would be to have vectorized class instead of a one-class system. Meaning, one image can have various attributes linked to it and fed into the model. Classes based on the image might be size (in percentage of image coverage) or colour. Classes based on the presented Pokémon could be type, generation, evolution state or region.

The following phenomena  were  found regardless of dataset: Even though the \ac{MSE} was not steadily decreasing after a certain amount of time the generated images  were  still improving. The quality of images was dependent on the class  were  images for some classes  were  more indicative of the training images than other classes. The images that showed the highest image quality for the \ac{CIFAR-10} dataset  were  images belonging to the class car, truck and ship. For the Pokémon dataset the body types showing the highest quality in generated images  were  single/multiple pair of wings and only head. Additionally, no significant difference in quality between images generated using \ac{EMA} compared to images where \ac{EMA} was not used can be seen. This is depicted in Figure \ref{fig:cifar10results}.

\section{Conclusion}
\label{sec:conclusion}
Increasing the dataset and using class dependent \ac{DDPM} has shown positive effects on the image quality in comparison to previous approaches. 
While the model was overall successful in generating Pokémon based on body type, the training was mainly impeded by the lack of hardware. The model was trained using an NVIDIA GeForce GTX 1650 with 4GB of dedicated GPU memory. This allowed only images of the size 34x34 to be trained on and generated. Additionally, the biggest batch size without exceeding the available space was 8 samples, which increased the training time and hindered the model from training on multiple samples at once. Future studies should aim to increase the size of the images to be trained on and implement other grouping methods or class encodings.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% hier Irden - zum Ende des Textes - die bibliographischen Referenzen
% eingebunden
%
% Insbesondere stehen die eigentlichen Informationen in der Datei
% ``bib.bib''
%
\newpage
\printbibliography[heading=bibintoc]
